 

### 2020-09-10 vertical-thermal-review.Rmd
update title

**Title:** Thermal sensitivity of canopy versus understory leaves: patterns, mechanisms, and ecological implications

**Authors (so far, not necessarily in final order):** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor,
Elsa Ordway,
Marielle Smith,
Tyeen Taylor,
Kristina J. Anderson-Teixeira^1,2^*

@@

>>>>

**Title:** Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

**Authors (so far, not necessarily in final order):** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor^3^,
Elsa Ordway,
Marielle Smith,
Tyeen Taylor,
Kristina J. Anderson-Teixeira^1,2^*

@@

3. Center for Geospatial Analytics; North Carolina State University; Raleigh, NC 27607, USA
